Single-fluorophore orientation determination with multiview polarized illumination: modeling and microscope design

### 2017-09-18 paper/paper/paper.tex
"total sample irradiance" -> "sample irradiance"

Figure \ref{fig:asymmetric-double} shows our results for dual-view asymmetric
light-sheet illumination designs. We used light-sheet illumination on both sides
and kept the objectives orthogonal so that the light sheet from one objective
illuminates the focal plane of the other objective. Then, we swept through the
NA of one objective while maximizing the NA of the other objective so that both
objectives would touch the cover slip and each other
($\alpha_1 + \alpha_2 = 90^{\circ}$ in Figure \ref{fig:asymmetric-double}a)). We
swept through the NA asymmetry and the sample-exposure asymmetry while keeping
the total sample irradiance constant, and found that symmetric designs are at a
local minimum of the median and MAD of the solid-angle uncertainty. We also
found that at extreme asymmetries where the exposure from the low-NA arm is much
larger than the exposure from the high-NA arm (top-left and bottom-right corners
of Figures \ref{fig:asymmetric-double}d) and e)) the median and MAD are
comparable to the symmetric light-sheet microscope. This means that if a very
high-NA objective is available and a low-NA objective can provide light sheet
illumination, this microscope will perform comparably with a dual-view
microscope with two medium-NA objectives. Note that this asymmetric exposure
configuration maximizes the use of the high-NA detection objective---if a
high-NA objective is available it should be used for detection as much as
possible. Figure \ref{fig:asymmetric-double} also shows that designs with
slightly asymmetric NA can trade off a low solid-angle uncertainty median for a
low solid-angle uncertainty MAD by changing the sample exposure ratio.

>>>>

Figure \ref{fig:asymmetric-double} shows our results for dual-view asymmetric
light-sheet illumination designs. We used light-sheet illumination on both sides
and kept the objectives orthogonal so that the light sheet from one objective
illuminates the focal plane of the other objective. Then, we swept through the
NA of one objective while maximizing the NA of the other objective so that both
objectives would touch the cover slip and each other
($\alpha_1 + \alpha_2 = 90^{\circ}$ in Figure \ref{fig:asymmetric-double}a)). We
swept through the NA asymmetry and the sample-exposure asymmetry while keeping
the sample irradiance constant, and found that symmetric designs are at a local
minimum of the median and MAD of the solid-angle uncertainty. We also found that
at extreme asymmetries where the exposure from the low-NA arm is much larger
than the exposure from the high-NA arm (top-left and bottom-right corners of
Figures \ref{fig:asymmetric-double}d) and e)) the median and MAD are comparable
to the symmetric light-sheet microscope. This means that if a very high-NA
objective is available and a low-NA objective can provide light sheet
illumination, this microscope will perform comparably with a dual-view
microscope with two medium-NA objectives. Note that this asymmetric exposure
configuration maximizes the use of the high-NA detection objective---if a
high-NA objective is available it should be used for detection as much as
possible. Figure \ref{fig:asymmetric-double} also shows that designs with
slightly asymmetric NA can trade off a low solid-angle uncertainty median for a
low solid-angle uncertainty MAD by changing the sample exposure ratio.
